Without loss of generality, any reduced ring is a field

### 2018-04-14 slides-munich2018.tex
typo (thanks to Matthias!)
typo
Begin of paper on generic freeness

\title{Without loss of generality, any reduced ring is a field}
\author{Ingo Blechschmidt}
\date{April 11th, 2018}

@@

  Oberseminar Mathematische Logik \\
  Ludwig-Maximilians-Universität München \\
  April 11th, 2018
  \par
\end{frame}

@@

  \hil{Lemma.} Let~$A$ be a ring. Let~$M$ be an~$A$-module with generating
  family~$(x_1,\ldots,x_n)$. Assume that the only element~$g \in A$ such that one of
  the~$x_i$ is an~$A[g^{-1}]$-linear combination in~$A[g^{-1}]$ of the other generators
  is~$g = 0$. Then~$M$ is free with~$(x_1,\ldots,x_n)$ as a basis.

@@

\begin{frame}{An explicit constructive proof}
  \justifying\small
  \hil{Theorem.} Let~$A$ be a reduced ring. Let~$B$ by a finitely
  generated~$A$-algebra. If zero is the only element~$f \in A$ such
  that~$B[f^{-1}]$ is finitely presented as an~$A[f^{-1}]$-algebra, then~$1 =
  0$ in~$A$.

>>>>

\title{Without loss of generality, any reduced ring is a field}
\author{Ingo Blechschmidt}
\date{April 11st, 2018}

@@

  Oberseminar Mathematische Logik \\
  Ludwig-Maximilians-Universität München \\
  April 11st, 2018
  \par
\end{frame}

@@

  \hil{Lemma.} Let~$A$ be a ring. Let~$M$ be an~$A$-module with generating
  family~$(x_1,\ldots,x_n)$. Assume that the only element~$g \in A$ such that one of
  the~$x_i$ is an~$A[g^{-1}]$-linear combination in~$M[g^{-1}]$ of the other generators
  is~$g = 0$. Then~$M$ is free with~$(x_1,\ldots,x_n)$ as a basis.

@@

\begin{frame}{An explicit constructive proof}
  \justifying\small
  \hil{Theorem.} Let~$A$ be a reduced ring. Let~$B$ be a finitely
  generated~$A$-algebra. If zero is the only element~$f \in A$ such
  that~$B[f^{-1}]$ is finitely presented as an~$A[f^{-1}]$-algebra, then~$1 =
  0$ in~$A$.
